### 2018-02-10 manuscript.Rnw
add figure (fig4). A handpicked subset of S1.
fixes #1

\begin{figure}[!h]
	\includegraphics[width=1\textwidth]{fig/fig-1.pdf}
	\caption{{\bf The \texttt{rethomics} workflow.}
		Diagram representing the interplay between, from left to right, the raw data, the \texttt{rethomics} packages (in blue) and the rest of the \texttt{R} ecosystem.}
	\label{fig:fig-1}
\end{figure}

@@

\begin{figure}[!h]
	\includegraphics[width=1\textwidth]{fig/fig-2.pdf}
	\caption{{\bf Example of a \texttt{behavr} table.}
		The metadata holds a single row for each of the $n$ individuals. 
		Its columns, the $p$ metavariables, are of two kind: either required and defined by the acquisition platform (\emph{i.e.} used to fetch the data) or user-defined (\emph{i.e.} arbitrary).
		In the data, each row is a ``read'' (\emph{i.e.} information about one individual at one time point).
		It is formed of $q$ variables and is expected to have a very large number of reads $k$ for each individual $i$.
		Data and metadata are implicitly joined with the \texttt{id} field.
		In this figure, the names used for variables and metavariable are only plausible examples that will likely differ in practice. 
	}
	\label{fig:fig-2}
\end{figure}

>>>>

\begin{figure}[!h]
	%\includegraphics[width=1\textwidth]{fig/fig-1.pdf}
	\caption{{\bf The \texttt{rethomics} workflow.}
		Diagram representing the interplay between, from left to right, the raw data, the \texttt{rethomics} packages (in blue) and the rest of the \texttt{R} ecosystem.}
	\label{fig:fig-1}
\end{figure}

@@

\begin{figure}[!h]
	%\includegraphics[width=1\textwidth]{fig/fig-2.pdf}
	\caption{{\bf \texttt{behavr} table.}
	A: Illustration of a \texttt{behavr} object, core data structure in \texttt{rethomics}.
		The metadata holds a single row for each of the $n$ individuals. 
		Its columns, the $p$ metavariables, are of two kind: either required and defined by the acquisition platform (\emph{i.e.} used to fetch the data) or user-defined (\emph{i.e.} arbitrary).
		In the data, each row is a ``read'' (\emph{i.e.} information about one individual at one time point).
		It is formed of $q$ variables and is expected to have a very large number of reads $k$ for each individual $i$.
		Data and metadata are implicitly joined with the \texttt{id} field.
		Names used for variables and metavariable are only plausible examples that will likely differ in practice. 
		B: Non exhaustive list of use of a \texttt{behavr} table, refered as \texttt{dt}. 
		In addition of operations on data inherited from \texttt{data.table}, we provide utilities designed specifically to act on both            metadata and data.  
	}
	\label{fig:fig-2}
\end{figure}
